---
title: "A comparison of the IMDB ratings of recent Dreamworks and 20th Century Fox movies"
author: "Ezra Herman"
date: "16/05/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(TOSTER)
library(dplyr)
library(tidyr)
```

# Theoretical hypothesis 
Recent movies by Dreamworks are as good as recent movies by 20th Century Fox.

# Dependent variable
The dependent variable is the IMDB score. Via the advanced title search, I searched for feature films with a release date to set to max 2019. I searched once for Dreamworks and once for 20th Century Fox. For each, the titles were sorted starting with the most recent release date.

# One observation was excluded
```{r load data, echo = FALSE}
data <- read.csv('../../originalDataAndMetaData/originalData/IYSIAssignment7DataRaw.csv', header = T)
```
One movie was found to have no ratings on IMDB (Thomas and The 2 Brothers). This observation was removed from the analysis, leaving 20th Century Fox with 33 instead of 34 observations.

# Statistical test suggests that recent Dreamworks and 20th Century Fox movies are equally good
```{r summary stats, echo = FALSE}
#Remove NAs
data <- data %>% drop_na()

#Calculate means and standard deviations
m1 <- mean(data$rating[which(data$company=="DreamWorks")])
m2 <- mean(data$rating[which(data$company=="20th Century Fox")])
sd1 <- sd(data$rating[which(data$company=="DreamWorks")])
sd2 <- sd(data$rating[which(data$company=="20th Century Fox")])
n1 <- length(data$rating[which(data$company=="DreamWorks")])
n2 <- length(data$rating[which(data$company=="20th Century Fox")])
```

For each company, the mean and standard deviation were computed (Dreamworks: mean = `r round(m1,2)`, sd = `r round(sd1,2)`; 20th Century Fox: mean = `r round(m2,2)`, sd = `r round(sd2,2)`). These were used to perform an equivalence test (\autoref{fig:TOSTtwo}). The null hypothesis of a mean difference equal or greater than a Cohen's d of 0.8 (equivalent to a raw difference of 0.6888) was rejected at the 5% level (mean difference = 0.248, 90% CI: [-0.103, 0.599], $t_{60.05}=-2.1$, $p=0.020$).  
&nbsp;&nbsp;&nbsp;&nbsp;&nbsp;It was not planned in the pre-registration to perform a null hypothesis significance test. Even though this is included in \autoref{fig:TOSTtwo}, it is not interpreted here.




```{r perform test, echo = FALSE, message = FALSE, results = FALSE, fig.keep = 'all', fig.cap="\\label{fig:TOSTtwo} The null hypothesis that the Cohen's d effect size is equal to or larger than 0.8 is rejected."}
#perform equivalence test
TOSTtwo(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2, n1 = n1, n2 = n2, low_eqbound_d = -0.8, high_eqbound_d = 0.8)
```


# Conclusion
Overall, this analysis suggests that the observed difference in ratings between recent Dreamworks and 20th Century Movies is statistically equivalent to 0, with an equivalence bound of Cohen's d of 0.8. Thus, it is concluded that recent Dreamworks and 20th Century Movies are likely not to largely differ in their average IMDB ratings, which supports the hypothesis that their recent movies are equally good.





